\documentclass[11pt]{article}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{makeidx}
\usepackage{graphicx, array}
\usepackage{pgf,tikz}
\usepackage{tkz-euclide}
\usetkzobj{all}
\usepackage{enumerate}
\usepackage[margin = 0.5in]{geometry}
\pagestyle{empty}
\raggedright

\begin{document}

Name \makebox[2.5in]{\hrulefill}    \hfill  Honors PreCalc P-Set  

\subsubsection*{Transforming Functions \hfill \makebox[0.35in]{\hrulefill} / 10}

For the following, describe how the graph of the function is a transformation of the original function.
\begin{flalign*}
1.  \quad   &   y=f(x)-2    &
2.  \quad   &   y=f(x)+7    &
3.  \quad   &   y=f(x-3)    &
4.  \quad   &   y=f(x+5)    &&\\[1.25in]
5.  \quad   &   y=5f(x)     &
6.  \quad   &   y=\frac{1}{3}f(x)   &
7.  \quad   &   y=-f(x)     &
8.  \quad   &   y=f(-x)     &&\\[1.25in]
9.  \quad   &   y=f(4x)     &
10. \quad   &   y=f\left(\frac{1}{2}x\right)    &
11. \quad   &   y=f(x+3)-7  &
12. \quad   &   y=f(2x)+5   &&\\[1.25in]
\end{flalign*}

Write the equation for the transformed function given each parent function.
\newline\\

13. The graph of $f(x)=\sqrt{x}$ is reflected over the $x$-axis and vertically stretched by a factor of 2.5    \\[1in]

14. The graph of $f(x)=|x|$ is horizontally compressed by a factor of 3.    \\[1in]

15. The graph of $f(x)=\dfrac{1}{x}$ is shifted 3 units right and 2 units down.

\newpage


\boxed{\textit{Level 2}}    \newline\\

16. Graph the functions $f(x)=5x+x^2$ and $g(x)=|5x+x^2|$. Describe what transformation(s) are done to the graph of $f(x)$ to obtain the graph of $g(x)$.   \\[0.75in]

17. Suppose the graph of $y=f(-2x)$ is given. Explain how to obtain the graph of $y=f(x)$.   \\[0.75in]

18. How is the graph of $f(x)=x^2+6x$ a transformation of the graph of $f(x)=x^2$.

% \boxed{\textit{Level 3}}    \newline\\


\newpage


\textbf{Transformation of Functions KEY}

\begin{enumerate}
    \item Shift down 2 units
    \item Shift up 7 units
    \item Shift right 3 units
    \item Shift left 5 units
    \item Vertical stretch by factor of 5
    \item Vertical compression by factor of 3
    \item Reflect across $x$-axis
    \item Reflect across $y$-axis
    \item Horizontal compression by factor of 4
    \item Horizontal stretch by factor of 2
    \item Shift left 3 units, shift down 7 units
    \item Horizontal compression by factor of 2, shift up 5 units
    \item $g(x) = -2.5\sqrt{x}$
    \item $g(x) = |3x|$
    \item $g(x) = \dfrac{1}{x-3} - 2$
\end{enumerate}

\end{document}
